Determining the direction of causality in the face of measurement error

### 2016-02-25 docs/manuscript.tex
updated analysis

\setlength{\droptitle}{-2em}
  \title{Determining the direction of causality in the face of measurement error}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{14 February 2016}

@@

With the explosion in data that measures the human phenome, of great
interest is understanding the causal nature of the emerging putitive
correlations between measures of interest. Mediation is a commonly used
statistical method for making causal inference in observational
data\textsuperscript{1--4}, and it exists in many forms, from simple
regression based systems to structural equation modeling. The principle
behind mediation analysis can be explained as follows. Supposing an
exposure has a causal effect on an outcome, then an `instrument' that
causes the exposure (a single nucleotide polymorophism (SNP), for
example) should also influence the outcome. Therefore the influence of
the instrument on the outcome conditional on the exposure should be
zero. This forms the basis of a number of methods, such as the causal
inference test (CIT)\textsuperscript{1}, which have been employed by a
number of recent publications make causal inferences, often in large
scale `omics datasets\textsuperscript{5--7}.

While mediation based approaches are simple and convenient to implement,
it is important to note where they may lead to unreliable results. One
such mechanism is measurement error\textsuperscript{8--11}. Measurement
(or observational) error is the difference between a measured value of a
quantity and its true value. Such variability can arise through a whole
plethora of mechanisms, which are often unique to the study design and
difficult to avoid\textsuperscript{12,13}. Array technology is now
commonly used to obtain high throughput phenotyping at low cost, but
they come with the problem of having imperfect sensitivity, so for
example methylation levels as measured by the Illumina450k chip are
prone to have some amount of noise around the true
value\textsuperscript{14,15}. Sensitivity is also an issue, for example
if the unit of measurement of biological interest is the methylation
level in a T cell, then measurement error of this value can be
introduced by using methylation levels from whole blood samples because
the measured value will be an assay of many cell
types\textsuperscript{16}.

Measurement error can indeed arise in more low-tech data too, for
example when measuring body mass index (BMI) one is typically interested
in using this as a proxy for obesity, but it is clear that the
correlation between BMI and obesity is not perfect\textsuperscript{17}.
A similar problem of biological misspecification is unavoidable in
disease diagnosis. Measurement error can also be introduced after the
data has been collected, for example the transformation of non-normal
data for the purpose of statistical analysis will lead to a new variable
that will typically have both bias and imprecision compared to the
original variable. The sources of measurement error are not limited to
this list\textsuperscript{13}, and its impact has been explored in the
context of mediation analysis in the epidemiological literature
extensively\textsuperscript{8,11}.

An alternative statistical method that gained prominence at least in
part as a solution to the problem of measurement
error\textsuperscript{18} is Mendelian randomisation
(MR)\textsuperscript{19,20}. Here an instrumental variable (typically a
SNP) that has a robost, causal association with the exposure is used to
proxy the exposure in an association test with the outcome. If there is
no measurement error in the SNP then the causal association between the
exposure and the outcome can be estimated by scaling the association
between the SNP and the outcome by the association between the SNP and
the exposure. This approach also has the useful property that it guards
against unmeasured confounders driving the association between exposure
and outcome; and if the biological effect of the SNP is understood then
it can also aid against reverse causality driving the association.

Here, however, arises a potential issue. Often the biological effect of
a SNP is not known, and therefore it can be difficult to determine for
which of the two variables in a putative exposure-outcome association is
the SNP a valid instrument. By definition, we expect that if the
association is causal then a SNP for the exposure will be associated
with the outcome, so if the researcher erroneously uses the SNP as an
instrument for the outcome then they are likely to see an apparently
robust causal association of outcome on exposure. Such a situation can
arise in many scenarios. For example genome wide association studies
(GWASs) that identify genetic associations for complex traits are by
design hypothesis free and agnostic of genomic function, and it often
takes years of follow up studies to understand the biological nature of
a putative GWAS hit\textsuperscript{21}. Another situation is where the
causal direction between 'omic measures need to be determined, for
example if a DNA methylation probe is associated with expression of an
adjacent gene, then is a cis-acting SNP an instrument for the DNA
methylation level, or the gene expression level\textsuperscript{7}?

@@

The analysis proceeds by simulating variables that have known causal
effects and valid instruments, and then applying measurement error in
different configurations. We then assess the performance of the CIT test
and MR analysis for a) inference of a causal relationship and b)
inferring the correct direction of causality. Included in the MR
analysis is a simple extension that is used to make inference of the
causal direction when it is unknown which of the correlated variables
the instrument is directly acting upon. All analysis was performed using
the R programming language\textsuperscript{22} and code is made
available at \href{}{github url to go here}.

@@

The CIT method\textsuperscript{1} is implemented in the R package
\emph{R/cit}\textsuperscript{23}. The \emph{cit.cp} function was used to
obtain an omnibus p-value of causality between an exposure \(x\) and an
outcome \(y\) using a mediator \(g\). To infer the direction of
causality using the CIT method, the omnibus p-value was estimated for
\(x\) causing \(y\), and for \(y\) causing \(x\), and the model that
returned the lowest p-value was taken as the one denoting the correct
causal direction.

@@

Supposing there are two correlated variables, \(x\) and \(y\), with a
variant \(g\) associated with both. Assuming no horizontal pleiotropy
(i.e. \(g\) only has an effect on one of the variables through the other
variable) it is desirable to know which of the variables it has a direct
influence on. This can be achieved by testing for a difference in the
correlations \(\rho_{g, x}\) and \(\rho_{g, y}\) using Steiger's Z-test
for correlated correlations within a population\textsuperscript{24}. It
is calculated as

@@

and a p-value is generated from the \(Z\) value to indicate confidence
of difference in correlations \(\rho_{gx}\) and \(\rho_{gy}\). The test
for a causal association is then obtained by performing two sample MR in
the direction that is predicted to be the correct model based on the Z
score test. For simplicity, the test is deemed to have obtained a robust
association if the Z score test has a p-value \(< 0.05\) and the two
sample MR analysis has a p-value \(< 0.05\). Note that the same approach
can be applied to a two-sample MR setting, where

@@

We performed simulations to explore the performance of this approach in
comparison to CIT. Figure 3 shows that, as predicted, when \(d < 0\) the
MR analysis is liable to infer the wrong direction of causality, and
that this erroneous result is more likely to occur with increasing
sample size. However, in all cases the MR analysis infers the wrong
direction of causality at the same or a lower rate than the CIT. When
\(d > 0\) is satisfied we observe that in many cases the MR method has
greater power to obtain evidence for causality than CIT, and always
obtains the correct direction of causality.

@@

\includegraphics{manuscript_files/figure-latex/cit_measurement_error_figure-1.pdf}\\
Figure 1: The CIT was performed on simulated variables where the
exposure influenced the outcome and the exposure was instrumented by a
SNP. The test statistic from CIT when testing if the exposure caused the
outcome (the true model) is in red, and the test for the outcome causing
the exposure (false model) is in green. Rows of plots represent the
sample sizes used for the simulations. As measurement error increases
(decreasing values on x-axis) the test statistic for the incorrect model
gets stronger and the test statistic for the correct model gets weaker.

@@

Figure 3: Outcomes were simulated to be causally influenced by
exposures, with varying degrees of measurement error applied to both.
CIT and MR were used to infer evidence for causality between the
exposure and outcome, and to infer the direction of causality. The value
of \(d = \rho_{x, x_O} - \rho_{x,y}\rho_{y,y_O}\), such that when \(d\)
is negative we expect the Steiger test to be more likely to be wrong
about the direction of causality. Rows of graphs represent the sample
size used in the simulations.

@@

5.Koestler, D. C. \emph{et al.} Integrative genomic analysis identifies
epigenetic marks that mediate genetic risk for epithelial ovarian
cancer. \emph{BMC medical genomics} \textbf{7,} 8 (2014).

6.Liu, Y. \emph{et al.} Epigenome-wide association data implicate DNA
methylation as an intermediary of genetic risk in rheumatoid arthritis.
\emph{Nature biotechnology} \textbf{31,} 142--7 (2013).

7.Waszak, S. M. \emph{et al.} Variation and genetic control of chromatin
architecture in humans. \emph{Cell} \textbf{162,} 1039--1050 (2015).

8.Cessie, S. le, Debeij, J., Rosendaal, F. R., Cannegieter, S. C. \&
Vandenbroucke, J. P. Quantification of bias in direct effects estimates
due to different types of measurement error in the mediator.
\emph{Epidemiology (Cambridge, Mass.)} \textbf{23,} 551--60 (2012).

9.Nagarajan, R. \& Scutari, M. Impact of noise on molecular network
inference. \emph{PloS one} \textbf{8,} e80735 (2013).

10.Shpitser, I., VanderWeele, T. \& Robins, J. On the validity of
covariate adjustment for estimating causal effects. \emph{Proceedings of
the Twenty Sixth Conference on Uncertainty in Artificial Intelligence
(UAI-10)} 527--536 (2010).

11.Blakely, T., McKenzie, S. \& Carter, K. Misclassification of the
mediator matters when estimating indirect effects. \emph{Journal of
epidemiology and community health} \textbf{67,} 458--66 (2013).

12.Houle, D., P{é}labon, C., Wagner, G. \& Hansen, T. Measurement and
meaning in biology. \emph{The Quarterly Review of Biology} \textbf{86,}
3--34 (2011).

13.Hern{á}n, M. a \& Cole, S. R. Invited Commentary: Causal diagrams and
measurement bias. \emph{American journal of epidemiology} \textbf{170,}
959--62; discussion 963--4 (2009).

14.Harper, K. N., Peters, B. a \& Gamble, M. V. Batch effects and
pathway analysis: two potential perils in cancer studies involving DNA
methylation array analysis. \emph{Cancer epidemiology, biomarkers \&
prevention : a publication of the American Association for Cancer
Research, cosponsored by the American Society of Preventive Oncology}
\textbf{22,} 1052--60 (2013).

15.Chen, Y.-a. \emph{et al.} Discovery of cross-reactive probes and
polymorphic CpGs in the Illumina Infinium HumanMethylation450
microarray. \emph{Epigenetics : official journal of the DNA Methylation
Society} \textbf{8,} 203--9 (2013).

16.Houseman, E. A. \emph{et al.} DNA methylation arrays as surrogate
measures of cell mixture distribution. \emph{BMC bioinformatics}
\textbf{13,} 86 (2012).

17.Ahima, R. S. \& Lazar, M. A. Physiology. The health risk of
obesity--better metrics imperative. \emph{Science (New York, N.Y.)}
\textbf{341,} 856--8 (2013).

18.Ashenfelter, O. \& Krueger, A. B. Estimates of the Economic Return to
Schooling from a New Sample of Twins. \emph{The American Economic
Review} \textbf{84,} 1157--1173 (1994).

19.{Davey Smith}, G. \& Ebrahim, S. Mendelian randomization: prospects,
potentials, and limitations. \emph{International journal of
epidemiology} \textbf{33,} 30--42 (2004).

20.{Davey Smith}, G. \& Hemani, G. Mendelian randomization: genetic
anchors for causal inference in epidemiological studies. \emph{Human
molecular genetics} \textbf{23,} R89-----R98 (2014).

21.Claussnitzer, M. \emph{et al.} FTO Obesity Variant Circuitry and
Adipocyte Browning in Humans. \emph{The New England journal of medicine}
\textbf{373,} 895--907 (2015).

22.R Core Team. \emph{R: A Language and Environment for Statistical
Computing}. (R Foundation for Statistical Computing, 2015). at
\textless{}\url{https://www.r-project.org/}\textgreater{}

23.Millstein, J. \emph{cit: Causal Inference Test. R package version
1.9}. (2016). at
\textless{}\url{http://cran.r-project.org/package=cit}\textgreater{}

24.Steiger, J. H. Tests for comparing elements of a correlation matrix.
\emph{Psychological Bulletin} \textbf{87,} 245--251 (1980).

>>>>

\setlength{\droptitle}{-2em}
  \title{Determining the direction of causality in the face of measurement error}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{25 February 2016}

@@

With the explosion in data that assess the human phenome, we are
presented with the challenge of understanding the causal nature of the
emerging putitive correlations between measures of interest. Mediation
is a commonly used statistical method for making causal inference in
observational data\textsuperscript{1--4}, and it exists in many forms,
from simple regression based systems to structural equation modeling
(SEM)\textsuperscript{5}. The principle behind mediation analysis can be
explained as follows. Supposing an exposure has a causal effect on an
outcome, then an `instrument' that causes the exposure (a single
nucleotide polymorophism (SNP), for example) should also influence the
outcome. Therefore the influence of the instrument on the outcome
conditional on the exposure should be zero. This forms the basis of a
number of methods, such as the regression-based causal inference test
(CIT)\textsuperscript{1}, an SEM implementation in the NEO
software\textsuperscript{5}, and various Bayesian methods, which have
been employed by a number of recent publications that make causal
inferences, often in large scale `omics datasets\textsuperscript{6--8}.

While mediation based approaches are simple and convenient to implement,
it is important to note where they may lead to unreliable results. One
such mechanism is measurement error\textsuperscript{9--12}, which has
been noted to be an explicit issue with CIT style
approaches\textsuperscript{13,14}. Measurement (or observational) error
is the difference between a measured value of a quantity and its true
value. Such variability can arise through a whole plethora of
mechanisms, which are often unique to the study design and difficult to
avoid\textsuperscript{15,16}. Array technology is now commonly used to
obtain high throughput phenotyping at low cost, but they come with the
problem of having imperfect sensitivity, so for example methylation
levels as measured by the Illumina450k chip are prone to have some
amount of noise around the true value\textsuperscript{17,18}.
Sensitivity is also an issue, for example if the unit of measurement of
biological interest is the methylation level in a T cell, then
measurement error of this value can be introduced by using methylation
levels from whole blood samples because the measured value will be an
assay of many cell types\textsuperscript{19}.

Measurement error will of course arise in more low-tech data too, for
example when measuring body mass index (BMI) one is typically interested
in using this as a proxy for obesity, but it is clear that the
correlation between BMI and underlying adiposity is not
perfect\textsuperscript{20}. A similar problem of biological
misspecification is unavoidable in disease diagnosis. Measurement error
can also be introduced after the data has been collected, for example
the transformation of non-normal data for the purpose of statistical
analysis will lead to a new variable that will typically have both bias
and imprecision compared to the original variable. The sources of
measurement error are not limited to this list\textsuperscript{16}, and
its impact has been explored in the context of mediation analysis in the
epidemiological literature extensively\textsuperscript{9,12}.

An alternative statistical method that gained prominence as a solution
to the problem of measurement error is Mendelian randomisation
(MR)\textsuperscript{21,22}. Here an instrumental variable (typically a
SNP) that has a robost, causal association with the exposure is used to
stand for the exposure in an association test with the outcome. If there
is no measurement error in the SNP then the causal association between
the exposure and the outcome can be estimated by scaling the association
between the SNP and the outcome by the association between the SNP and
the exposure. Indeed this approach was in part pioneered (in the form of
instrumental variable (IV) analysis) as a correction for measurement
error\textsuperscript{23}, but it also has the useful property that it
guards against unmeasured confounders driving the association between
exposure and outcome; and if the biological effect of the SNP is
understood then it can also aid against reverse causality driving the
association.

Here, however, arises a potential issue: often the biological effect of
a SNP is not known. If there exists a putative association between two
variables, with a SNP being robustly associated with each, it can be
difficult to determine which of the two variables is subject to the
direct effect of the SNP (i.e., for which of the two variables is the
SNP a valid instrument?). By definition, we expect that if the
association is causal then a SNP for the exposure will be associated
with the outcome, so if the researcher erroneously uses the SNP as an
instrument for the outcome then they are likely to see an apparently
robust causal association of outcome on exposure. Such a situation can
arise in many scenarios. For example genome wide association studies
(GWASs) that identify genetic associations for complex traits are, by
design, hypothesis free and agnostic of genomic function, and it often
takes years of follow up studies to understand the biological nature of
a putative GWAS hit\textsuperscript{24}. Another situation is where the
causal direction between 'omic measures need to be determined, for
example if a DNA methylation probe is associated with expression of an
adjacent gene, then is a cis-acting SNP an instrument for the DNA
methylation level, or the gene expression level\textsuperscript{8}?

@@

The analysis proceeds by simulating variables that have known causal
effects and valid instruments, and then applying measurement error in
different configurations. We then assess the performance of the CIT test
and MR analysis for a) inference of a causal relationship and b)
inferring the correct direction of causality. Included in the MR
analysis is a simple extension that is used to make inference of the
causal direction when it is unknown which of the correlated variables
the instrument is directly acting upon. All analysis was performed using
the R programming language\textsuperscript{25} and code is made
available at \href{}{github url to go here}.

@@

The CIT method\textsuperscript{1} is implemented in the R package
\emph{R/cit}\textsuperscript{26}. The \emph{cit.cp} function was used to
obtain an omnibus p-value of causality between an exposure \(x\) and an
outcome \(y\) using a mediator \(g\) by making inferences based on a
number of conditions that we examine in the results. To infer the
direction of causality using the CIT method, an omnibus p-value
generated by CIT, \(p_{CIT}\), was estimated for the correct model of
\(x\) causing \(y\), and for incorrect model of \(y\) causing \(x\). For
some significance threshold \(\alpha\), causal direction was inferred
based on the following scenarios:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  If \(p_{CIT,correct} < \alpha\) and \(p_{CIT,incorrect} > \alpha\)
  then the correct model is accepted
\item
  If \(p_{CIT,correct} > \alpha\) and \(p_{CIT,incorrect} < \alpha\)
  then the incorrect model is accepted
\item
  If \(p_{CIT,correct} > \alpha\) and \(p_{CIT,incorrect} > \alpha\)
  then the an alternative causal model is accepted
\item
  If \(p_{CIT,correct} < \alpha\) and \(p_{CIT,incorrect} < \alpha\)
  then no inference is made
\end{enumerate}

For the purposes of compiling simulation results we use an arbitrary
\(\alpha = 0.05\) value.

@@

Supposing there are two correlated variables, \(x\) and \(y\), with a
variant \(g\) associated with both. Assuming no horizontal pleiotropy
(i.e. \(g\) only has an effect on one of the variables through the other
variable) it is desirable to know which of the variables it has a direct
influence on. This can be achieved by testing for a difference in the
correlations \(\rho_{g, x}\) and \(\rho_{g, y}\) using Steiger's Z-test
for correlated correlations within a population\textsuperscript{27}. It
is calculated as

@@

and a p-value is generated from the \(Z\) value to indicate confidence
of difference in correlations \(\rho_{gx}\) and \(\rho_{gy}\). The test
for a causal association is then obtained by performing two sample MR in
the direction that is predicted to be the correct model based on the Z
score test. For the purposes of compiling simulation results, the test
is deemed to have obtained a robust association if the Z score test has
a p-value \(< 0.05\) and the two sample MR analysis has a p-value
\(< 0.05\), though in practice we do not advocate using an arbitrary
\(p\) value threshold for denoting significance in making causal
inference.

Note that the same correlation test approach can be applied to a
two-sample MR\textsuperscript{28} setting, where the Steiger test of two
independent correlations is applied instead of the case detailed here
where correlations share one variable in common. An advantage of using
the Steiger test in the two sample context is that it can compare
correlations in independent samples where sample sizes are different.

@@

We performed simulations to explore the performance of this approach in
comparison to CIT. Figure 3 shows that, as predicted, when \(d < 0\) the
MR analysis is liable to infer the wrong direction of causality, and
that this erroneous result is more likely to occur with increasing
sample size. However, in a large number of cases the MR analysis infers
the wrong direction of causality at a much lower rate than the CIT. When
\(d > 0\) is satisfied we observe that in most cases the MR method has
greater power to obtain evidence for causality than CIT, and always
obtains the correct direction of causality.

@@

\includegraphics{manuscript_files/figure-latex/cit_measurement_error_figure-1.pdf}

Figure 1: The CIT was performed on simulated variables where the
exposure influenced the outcome and the exposure was instrumented by a
SNP. The test statistic from CIT when testing if the exposure caused the
outcome (the true model) is in red, and the test for the outcome causing
the exposure (false model) is in green. Rows of plots represent the
sample sizes used for the simulations. As measurement error increases
(decreasing values on x-axis) the test statistic for the incorrect model
gets stronger and the test statistic for the correct model gets weaker.

@@

\includegraphics{manuscript_files/figure-latex/cit_mr_comparison_figure-1.pdf}

Figure 3: Outcomes were simulated to be causally influenced by
exposures, with varying degrees of measurement error applied to both.
CIT and MR were used to infer evidence for causality between the
exposure and outcome, and to infer the direction of causality. The value
of \(d = \rho_{x, x_O} - \rho_{x,y}\rho_{y,y_O}\), such that when \(d\)
is negative we expect the Steiger test to be more likely to be wrong
about the direction of causality. Rows of graphs represent the sample
size used in the simulations. For the CIT method, outcome 1 denoted
evidence for causality with correct model, outcomes 2 or 3 denoted
evidence for causality with incorrect model, and outcome 4 denoted no
evidence for causality.

@@

5.Aten, J. E., Fuller, T. F., Lusis, A. J. \& Horvath, S. Using genetic
markers to orient the edges in quantitative trait networks: the NEO
software. \emph{BMC systems biology} \textbf{2,} 34 (2008).

6.Koestler, D. C. \emph{et al.} Integrative genomic analysis identifies
epigenetic marks that mediate genetic risk for epithelial ovarian
cancer. \emph{BMC medical genomics} \textbf{7,} 8 (2014).

7.Liu, Y. \emph{et al.} Epigenome-wide association data implicate DNA
methylation as an intermediary of genetic risk in rheumatoid arthritis.
\emph{Nature biotechnology} \textbf{31,} 142--7 (2013).

8.Waszak, S. M. \emph{et al.} Variation and genetic control of chromatin
architecture in humans. \emph{Cell} \textbf{162,} 1039--1050 (2015).

9.Cessie, S. le, Debeij, J., Rosendaal, F. R., Cannegieter, S. C. \&
Vandenbroucke, J. P. Quantification of bias in direct effects estimates
due to different types of measurement error in the mediator.
\emph{Epidemiology (Cambridge, Mass.)} \textbf{23,} 551--60 (2012).

10.Nagarajan, R. \& Scutari, M. Impact of noise on molecular network
inference. \emph{PloS one} \textbf{8,} e80735 (2013).

11.Shpitser, I., VanderWeele, T. \& Robins, J. On the validity of
covariate adjustment for estimating causal effects. \emph{Proceedings of
the Twenty Sixth Conference on Uncertainty in Artificial Intelligence
(UAI-10)} 527--536 (2010).

12.Blakely, T., McKenzie, S. \& Carter, K. Misclassification of the
mediator matters when estimating indirect effects. \emph{Journal of
epidemiology and community health} \textbf{67,} 458--66 (2013).

13.Wang, L. \& Michoel, T. Detection of regulator genes and eQTLs in
gene networks. \emph{arXiv} \textbf{arXiv:1512,} (2015).

14.Lagani, V., Triantafillou, S., Ball, G., Tegner, J. \& Tsamardinos,
I. in \emph{Uncertainty in biology: A computational modeling approach}
47 (Springer, 2015). at
\textless{}\url{https://books.google.com/books?id=8SLUCgAAQBAJ\{/\&\}pgis=1}\textgreater{}

15.Houle, D., P{é}labon, C., Wagner, G. \& Hansen, T. Measurement and
meaning in biology. \emph{The Quarterly Review of Biology} \textbf{86,}
3--34 (2011).

16.Hern{á}n, M. a \& Cole, S. R. Invited Commentary: Causal diagrams and
measurement bias. \emph{American journal of epidemiology} \textbf{170,}
959--62; discussion 963--4 (2009).

17.Harper, K. N., Peters, B. a \& Gamble, M. V. Batch effects and
pathway analysis: two potential perils in cancer studies involving DNA
methylation array analysis. \emph{Cancer epidemiology, biomarkers \&
prevention : a publication of the American Association for Cancer
Research, cosponsored by the American Society of Preventive Oncology}
\textbf{22,} 1052--60 (2013).

18.Chen, Y.-a. \emph{et al.} Discovery of cross-reactive probes and
polymorphic CpGs in the Illumina Infinium HumanMethylation450
microarray. \emph{Epigenetics : official journal of the DNA Methylation
Society} \textbf{8,} 203--9 (2013).

19.Houseman, E. A. \emph{et al.} DNA methylation arrays as surrogate
measures of cell mixture distribution. \emph{BMC bioinformatics}
\textbf{13,} 86 (2012).

20.Ahima, R. S. \& Lazar, M. A. Physiology. The health risk of
obesity--better metrics imperative. \emph{Science (New York, N.Y.)}
\textbf{341,} 856--8 (2013).

21.{Davey Smith}, G. \& Ebrahim, S. Mendelian randomization: prospects,
potentials, and limitations. \emph{International journal of
epidemiology} \textbf{33,} 30--42 (2004).

22.{Davey Smith}, G. \& Hemani, G. Mendelian randomization: genetic
anchors for causal inference in epidemiological studies. \emph{Human
molecular genetics} \textbf{23,} R89-----R98 (2014).

23.Ashenfelter, O. \& Krueger, A. B. Estimates of the Economic Return to
Schooling from a New Sample of Twins. \emph{The American Economic
Review} \textbf{84,} 1157--1173 (1994).

24.Claussnitzer, M. \emph{et al.} FTO Obesity Variant Circuitry and
Adipocyte Browning in Humans. \emph{The New England journal of medicine}
\textbf{373,} 895--907 (2015).

25.R Core Team. \emph{R: A Language and Environment for Statistical
Computing}. (R Foundation for Statistical Computing, 2015). at
\textless{}\url{https://www.r-project.org/}\textgreater{}

26.Millstein, J. \emph{cit: Causal Inference Test. R package version
1.9}. (2016). at
\textless{}\url{http://cran.r-project.org/package=cit}\textgreater{}

27.Steiger, J. H. Tests for comparing elements of a correlation matrix.
\emph{Psychological Bulletin} \textbf{87,} 245--251 (1980).

28.Pierce, B. L. \& Burgess, S. Efficient design for Mendelian
randomization studies: subsample and 2-sample instrumental variable
estimators. \emph{American journal of epidemiology} \textbf{178,}
1177--84 (2013).
